Connectome inferences using partial correlation from imaging calcium signal

### 2014-06-13 article.tex
typos

% Datasets
To assess our method, we have used four datasets provided by the organizer
of the Connectomics challenge : \textit{normal-1, normal-2, normal-3, normal-4}.
Those datasets are time series of size $T=179500$ of image calcium from simulated
neuronal network \cite{stetter2012model} with $|V|=1000$ neurons. The networks
to inferred have around 15000 edge and are similar to those
used to rank challenge participants. Note that our parameter tuning was mainly
done on the \textit{normal-1} dataset and partly on \textit{normal-4} dataset,
therefore it may justify why these networks are better retrieved despite the
fact that some might be simpler to infer.

% Metrics : ROC AUC and AUPRC
In supervised learning terms, the network inference task can be viewed as a
binary classification task where one has to correctly classified the presence
or the absence of edges of the graph. Given the ground true adjacency matrix
$A$ and a connectivity score matrix $\hat{A}$, we assess the accuracy of the
network inference method using the area under the ROC curve (ROC AUC)
and the area under the precision-recall curve (AUPRC)
(\cite{schrynemackers2013protocols}). Since neurons are not self-connected
($(i, i) \not \in E, \forall i \in V$) and some inference methods could
give maximal scores to the diagonal of $\hat{A}$, e.g. Pearson
correlation, we set those elements to the minimum of $\hat{A}$ prior evaluating
those algorithms.

>>>>

% Datasets
To assess our method, we have used four datasets provided by the organizers
of the Connectomics challenge : \textit{normal-1, normal-2, normal-3, normal-4}.
Those datasets are time series of size $T=179500$ of image calcium from simulated
neuronal networks (\cite{stetter2012model}) with $|V|=1000$ neurons. The networks
to inferred have around 15000 edges and are similar to those
used to rank challenge participants. Note that our parameter tuning was mainly
done on the \textit{normal-1} dataset and partly on \textit{normal-4} dataset,
therefore it may justify why these networks are better retrieved despite the
fact that some might be simpler to infer.

% Metrics : ROC AUC and AUPRC
In supervised learning terms, the network inference task can be viewed as a
binary classification task where one has to correctly classify the presence
or the absence of edges of the graph. Given the ground true adjacency matrix
$A$ and a connectivity score matrix $\hat{A}$, we assess the accuracy of the
network inference method using the area under the ROC curve (ROC AUC)
and the area under the precision-recall curve (AUPRC)
(\cite{schrynemackers2013protocols}). Since neurons are not self-connected
($(i, i) \not \in E, \forall i \in V$) and some inference methods could
give maximal scores to the diagonal of $\hat{A}$, e.g. Pearson
correlation, we set those elements to the minimum of $\hat{A}$ prior evaluating
those algorithms.
